Human Activity Recognition using Machine Learning
========================================================

We will create a Machine Learning model to distinguish between 

## Initial Processing

We load the training and testing data, fit a Random Forest model (rf) predicting the classe variable using 50% of the observations, using only the variables without missing data. We save the model in a file for later use, due to the great time spent in the calculation.


```{r cache = TRUE}
library(caret)
data <- read.csv("pml-training.csv")
datest <- read.csv("pml-testing.csv")
removeIndex <- grep("timestamp|X|user_name|new_window",names(data))
data <- data[,-removeIndex]
datest <- datest[,-removeIndex]

data <- data[,which(colSums(is.na(datest))==0)]
datest <- datest[,which(colSums(is.na(datest))==0)]

inTrain <- createDataPartition(data$classe, p = 1/2)[[1]]
training <-  data[ inTrain,]
testing <-  data[-inTrain,]
```
```{r cache=TRUE, eval=FALSE}
modRF <- train(classe ~.,data=training,method="rf")
save(modRF,file=".modRF")
```

In order to check the model, we take the testing data (50% of total) and compare the prediction and the real classe. This allows us to cross-validate, and find that the accuracy of the model. 

We compute the confusion matrices of the model with the out of sample data:
```{r cache=TRUE}
load(".modRF")
pred <- predict(modRF,testing)
conf <- confusionMatrix(testing$classe, pred)

conf
```

Thus, using cross validation, we therefore estimate the out-of-sample accuracy as 99%, just like the confusion matrix shows.

